\mytitle

### 2020-04-19 paper.tex
evaluation.

In this section, we 
present an empirical evaluation of our quadratic models based on 
standard WFLO instances.
Our main results are: \begin{itemize}
	\item QUBO based WFLO using the digital annealer provides state-of-the-art results in seconds.
	\item Given enough time LS quadratic models are superior to both linear models and to an SS approximations. 
\end{itemize}
We start by outlining the experimental design of our evaluation, followed by a presentation of our main results
and a discussion of the results together with the limitations of the approach.

@@

\paragraph{WFLO Instances}
\begin{figure}[t]
	\centering
	\includegraphics[scale = 0.3]{prob_wind_pdf.pdf}

@@

\paragraph{Experimental Setting}

>>>>

In this section, we 
present an empirical evaluation of the two quadratic models based on 
standard WFLO instances.
Our main results are: \begin{itemize}
	\item QUBO based WFLO using the digital annealer is competitive with exact methods. 
	\item Given sufficient runtime the QCOP model provides superior results compared to state-of-the-art methods.
	\item The runtime for solving the QUBO model is two orders of magnitude lower than QCOP. 
\end{itemize}
We start by outlining the experimental design of our evaluation, followed by a presentation of our main results
and a discussion of the results together with the limitations of the approach.

@@

\paragraph{WFLO Setting and Measurements}

To test and benchmark our models, we used 12 standard benchmark WFLO instances
from the literature~\cite{MOSETTI1994105,Zhang2014,grady2005placement}. 
The 12 benchmarks result from varying 2 wind settings (1 and 36 wind directions),
2 grid sizes ($10\times10$ with cell size $200$ meters and $20\times20$ with cell size $100$ meters),
and 3 variations for number of turbines ($m \in \{20, 30 or 40\}$).
The wind regime distribution presented in Figure~\ref{fig:prob_wind} was 
elicited from~\cite{Zhang2014}.
Additional parameters that were used to calculate 
the velocities ($u_{id\infty}, u_{ijd}$) include: turbine height ($60$ meters),
ground roughness ($0.3$ meters), turbine rotor radius ($20$ meters), and a wind farm of size $2km \times 2km$.
We have measured solutions using the SS energy expression.
To to this end, we converted solutions that came from LS based methods into the corresponding SS expression.
Lastly, the total mean energy is presented in $kW/year$.

\begin{figure}[t]
	\centering
	\includegraphics[scale = 0.3]{prob_wind_pdf.pdf}

@@

We compared our two models, namely QCOP and QUBO, against two state of the art exact optimization methods:
the integer linear programming (ILP-LS) approach from~\cite{donovan2005wind}, and the 
model that uses a quadratic approximation (QP-SS)~\cite{turner2014new}. The CP approach presented in~\cite{Zhang2014} was
reported to perform worse than the rest and was left out of the experiments.
We used state of the art software, namely Gurobi~\cite{gurobi}, to solve QCOP, ILP-SS and QP-SS, and 
applied both Fujitsu's digital annealer and GUrobi to solve QUBO.

\paragraph{Experimental Procedure}

\todo{Explain how we solved WFLO using the various instances}
